---
title: "NF-OSI Data Sharing Plan (GFF GTI)"
author: "NF-OSI DCC"
date: ""
output:
  html_document:
    includes:
      in_header: ../header.html
      after_body: ../footer.html 
    theme: paper
    css: ../www/style.css
  pdf_document:
    includes:
      in_header: ../inline_style.tex
params:
  fundingAgencyFullName: Gilbert Family Foundation (GFF)
  fundingAgency: GFF
  embargoPeriod: 18 months
---

```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r include_dsp_common, child = '../preamble_commitment_data_sharing.Rmd'}
```

```{r include_dsp_common, child = '../preamble_data_sharing.Rmd'}
```


## Data Licensing

By default, upon public release, data will be made available under Conditions for Use requiring data users to agree to use the data solely for advancing research in the field of diagnosis, prevention, treatment and/or cure of NF, or conditions or complications caused by NF, including visual impairment caused by NF optic pathway gliomas. Subject to any required institutional approval, a data contributor can alternatively opt to release the data using a Creative Commons license such as CC0, which is equivalent to depositing the data into the public domain. 

```{r include_dsp_common, child = '../dsp_common.Rmd'}
```

```{r include_addendum_1, child = if(FALSE) '../addendum_1.Rmd'}
```

```{r include_addendum_2, child = if(FALSE) '../addendum_2.Rmd'}
```
